---
title: "Weekly exercise 4"
output: 
  learnr::tutorial:
    theme: "sandstone"
    css: css/styles.css
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library("learnr")
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
```

## Question 4 a)

The following code draws a black circle with radius $1$ and a red circle with radius $1/2$, both centred at the coordinate $(0,0)$. 

```{r echo=TRUE}
library(ggplot2)
circles <- ggplot() +
  theme_void() +
  geom_function(fun = function(x) sqrt(1 - x^2), xlim = c(-1, 1)) +
  geom_function(fun = function(x) -sqrt(1 - x^2), xlim = c(-1, 1)) +
  geom_function(fun = function(x) sqrt(1/4 - x^2), xlim = c(-.5, .5),
                color = "red") +
  geom_function(fun = function(x) -sqrt(1/4 - x^2), xlim = c(-.5, .5),
                color = "red") +
  annotate("point", x = 0, y = 0) +
  coord_equal()
```


Recall $(X,Y)$ and $(X_2,Y_2)$ from Question 2. Below are 1,000 simulated points from  $(X,Y)$. 

```{r echo=FALSE}
set.seed(237)
N <- 1000
r <- sqrt(runif(N))
theta <- runif(N, max = 2 * pi) 
circles +
  geom_point(aes(x = r * cos(theta), y = r * sin(theta)),
             alpha = .7)
```


Using the 1,000 points, the estimated probability of landing inside the red circle is `r round(sum(r < .5) / N, 3)`.

Simulate 1,000 points from $(X_2, Y_2)$ and estimate the probability that it lands inside the red circle. The plot object `circles` is available in the following exercise code chunk.

```{r q5a-setup}
library(ggplot2)
circles <- ggplot() +
  theme_void() +
  geom_function(fun = function(x) sqrt(1 - x^2), xlim = c(-1, 1)) +
  geom_function(fun = function(x) -sqrt(1 - x^2), xlim = c(-1, 1)) +
  geom_function(fun = function(x) sqrt(1/4 - x^2), xlim = c(-.5, .5),
                color = "red") +
  geom_function(fun = function(x) -sqrt(1/4 - x^2), xlim = c(-.5, .5),
                color = "red") +
  annotate("point", x = 0, y = 0) +
  coord_equal()
```

```{r q5a, exercise=TRUE, exercise.lines=15, fig.aps=1}
N <- 1000
circles
```


```{r}
shiny::textInput(
  "q4a", "What is the estimated probability?", width = "100%")
```


## Question 4 b)

The following code creates a data frame representing
a deck of playing cards. The data frame is named `deck` and is available in the exercise code chunk.

```{r echo=TRUE}
suits <- c("Spades", "Hearts", "Clubs", "Diamonds")
numbers <- c("A", 2:10, "J", "Q", "K")
values <- c(11, 2:10, 10, 10, 10)
deck <- data.frame(
  suit = rep(suits, each = 13),
  number = rep(numbers, 4),
  value = rep(values, 4)
)
```

```{r q4b-setup}
suits <- c("Spades", "Hearts", "Clubs", "Diamonds")
numbers <- c("A", 2:10, "J", "Q", "K")
values <- c(11, 2:10, 10, 10, 10)
deck <- data.frame(
  suit = rep(suits, each = 13),
  number = rep(numbers, 4),
  value = rep(values, 4)
)
```

Generate 1,000 simulates of the following game played by one person.

_Game step:_

i. From a randomly shuffled single deck, you draw 2 cards without replacement.
ii. Sum the values of the cards based on the counting rule described below. If the count is less than $17$ go to step iii. Otherwise, __end the game__.
iii. Draw an extra card from the remaining deck. 

  
_Counting rule:_

+ Counts are based on the `number`s.
+ Values between `2` and `10` are always counted as is.
+ Consider the face cards where the `number` is `J`, `Q`, or `K` as $10$.
+ Consider `A` as $11$ if the resulting total is less than $22$. Otherwise, consider `A` as $1$.
+ The "default" values are stored in `value` column of the data frame `deck`. `A` stored as $11$.

Let $S$ be the sum of the values you have on your hands at the end of the game. Draw a histogram of the simulated values of $S$ with `binwidth = 1` and estimate $P(S>21)$, $E[S]$, and $\text{Var}(S)$.


```{r q4b, exercise=TRUE, exercise.line=20}
N <- 1000
S <- numeric(N)
for (i in seq_len(N)) {
  
}
deck
```

```{r}
shiny::textInput(
  "q4b1", "What is the estimated probability?", width = "100%")
```

```{r}
shiny::textInput(
  "q4b2", "What is the estimated expectation?", width = "100%")
```

```{r}
shiny::textInput(
  "q4c", "What is the estimated variance?", width = "100%")
```


