---
title: "Weekly exercise 5"
output: 
  learnr::tutorial:
    theme: "sandstone"
    css: css/styles.css
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library("learnr")
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
```

## Question 5 a)

Consider the estimator $T_n$ for $A$ identified in Question 4 c).

i. Simulate $m=100$ copies of $T_n$ with $n=10\ 000$. 
ii. Estimate $P\left(\lvert T_n-A \rvert>0.5\right)$ using the simulated copies and compare the estimate to the upper bound based on Chebyshev's inequality.
iii. Plot a histogram of the simulated values with `binwidth = .25` and `fill = abs(sims - A) > .5` inside `aes()` to highlight the simulated values that are more than $0.5$ away from the true value of $A$.

```{r q5a, exercise=TRUE, exercise.lines= 25}
A <- {{  }}
N <- 10000
m <- 100
sims <- {{ }} * {{ }}(N ,1/10)
{{ }}(sims) / N
```

```{r}
shiny::textAreaInput(
  "q5a", "What is the estimated probability of the estimator being more than 0.5 away from the true value? Compare it to the upper bound basaed on Chebyshev's inequality.", width = "100%", height = "150px")
```


## Question 5 b)

The following code creates a data frame representing a deck of playing cards
and a set of functions you can use for coding a game of Blackjack.

+ `deck` contains a data frame of 52 playing cards.
+ `score_blackjack()` returns of the current hand. It requires a subset of 
the `deck` as its input argument to represent the current hand.
+ `dealer()` returns `TRUE` when the dealer needs to draw one more card
based on the current hand. It requires a subset of the `deck` as its input
argument to represen the current hand.


```{r echo=TRUE, eval=FALSE}
suits <- c("Spades", "Hearts", "Clubs", "Diamonds")
numbers <- c("A", 2:10, "J", "Q", "K")
values <- c(11, 2:10, 10, 10, 10)
deck <- data.frame(
  suit = rep(suits, each = 13),
  number = rep(numbers, 4),
  value = rep(values, 4)
)
score_blackjack <- function(cards) {
  s <- sum(cards$value)
  n_aces <- sum(cards$value == 11)
  s <- s - 10 * min(ceiling(max(0, (s - 21) / 10)), n_aces)
  return(s)
}
dealer <- function(cards) {
  decision <- score_blackjack(cards) < 17
  return(decision)
}
winner <- function(player_score, dealer_score) {
  player_won <- TRUE
  if (dealer_score < 22 && dealer_score > player_score) {
    player_won <- FALSE
  }
  if (player_score > 21) {
    player_won <- FALSE
  }
  return(player_won)
}
```

Simulate $1,000$ iterations of **2** consecutive rounds of a game with a single player
against the dealer using a single deck. For the player, implement one of the
following strategies:

1. Develop your own strategy that takes the player's current and the dealer's first card as inputs. Remember that the player is blind to the dealer's second card until the player finalizes their hands.
2. Take one more card if the player's current score is less than $17$ AND the dealer's first card is greater than $7$.

Define $X_1$ and $X_2$ such that $X_i=1$ when the player wins $i$th round and $0$ otherwise. Estimate $E[X_1]$, $E[X_2]$, and $E[X_1X_2]$. Is it a reasonable conclusion that $X_1$ and $X_2$ are independent? Justify your answer using the estimates and the implemented strategy.


```{r q5b-setup}
suits <- c("Spades", "Hearts", "Clubs", "Diamonds")
numbers <- c("A", 2:10, "J", "Q", "K")
values <- c(11, 2:10, 10, 10, 10)
deck <- data.frame(
  suit = rep(suits, each = 13),
  number = rep(numbers, 4),
  value = rep(values, 4)
)
score_blackjack <- function(cards) {
  s <- sum(cards$value)
  n_aces <- sum(cards$value == 11)
  s <- s - 10 * min(ceiling(max(0, (s - 21) / 10)), n_aces)
  return(s)
}
dealer <- function(cards) {
  decision <- score_blackjack(cards) < 17
  return(decision)
}
winner <- function(player_score, dealer_score) {
  player_won <- TRUE
  if (dealer_score < 22 && dealer_score > player_score) {
    player_won <- FALSE
  }
  if (player_score > 21) {
    player_won <- FALSE
  }
  return(player_won)
}
```

```{r q5b, exercise=TRUE, exercise.lines=50}
N <- 1000
X1 <- numeric(N)
X2 <- numeric(N)
player <- function(player_cards, dealer_card) {
  # implement your own strategy
  return(decision)
}
play_a_round <- function(shuffled, position = 1) {
  # takes shuffled deck and the current position
  # of the top of the undealt deck as input arguments
  # deal first pairs
  # feel free to modify the function as needed
  player_hand <- c(position, position + 1)
  dealer_hand <- c(position + 2:3)
  position <- position + 4
  while (player(shuffled[player_hand, ], shuffled[dealer_hand[1], ])) {
    player_hand <- c(player_hand, position)
    position <- position + 1
  }
  player_score <- score_blackjack(shuffled[player_hand, ])
  if (player_score == 21) {
    return(c(TRUE, position)) # player wins immediately
  }
  if (player_score > 21) {
    return(c(FALSE, position)) # player loses immediately
  }
  while (dealer(shuffled[dealer_hand, ])) {
    dealer_hand <- c(dealer_hand, position)
    position <- position + 1
  }
  dealer_score <- score_blackjack(shuffled[dealer_hand, ])
  # return c(winner, current position)
  return(c(winner(player_score, dealer_score), position))
}

```


```{r}
shiny::textAreaInput(
  "q5b", "Is it a reasonable conclusion that the two random variables are independent? Justify your answer using the estimates and the implemented strategy.", width = "100%", height = "150px")
```
